Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-11 paper.Rnw
reorganized again and wrote code for moving the files to the submission folder

# Apply LIME with various tuning parameters to the sine data
if (!file.exists("data-sine-lime-explain.rds")) {

@@

    saveRDS(sine_lime_explain, "data-sine-lime-explain.rds")

@@

    sine_lime_explain <- readRDS("data-sine-lime-explain.rds")

@@

# Load the bullet matching training data and make some adjustments:
#   1. filter out observations known to have tank rash
#   2. exclude features not used to train the rtrees random forest 
#   3. add a case variable
#   4. change the name of the same_source variable to match the test data
#   5. reorder the variables
bullet_train <-
  readr::read_csv("data-bullet-train.csv.zip") %>%
  filter(!(
    land_id1 %in% c(
      "Hamby173-Br6-B2-L1",
      "Hamby173-Br9-B2-L4",
      "Hamby173-BrUnk-BB-L2",
      "Hamby173-BrUnk-BQ-L4"
    ) |
      land_id2 %in% c(
        "Hamby173-Br6-B2-L1",
        "Hamby173-Br9-B2-L4",
        "Hamby173-BrUnk-BB-L2",
        "Hamby173-BrUnk-BQ-L4"
      )
  )) %>%
  select(-lag, -abs_lag, -overlap, -signature_length) %>%
  mutate(case = factor(1:n())) %>%
  rename("samesource" = "same_source") %>%
  select(case, land_id1, land_id2, everything())

# Load the bullet test data
bullet_test <- readr::read_csv("data-bullet-test.csv.zip")

@@

# Convert the bullet figure to eps (if needed)
if (!file.exists("figure-08-1.eps")) {
  unzip("figure-08-1.png.zip")
  bullets <- image_read("figure-08-1.png")
  image_write(bullets, path = "figure-08-1.eps", format = "eps")
}

# Load and print the plot
knitr::include_graphics("figure-08-1.eps")

@@

# Load the signatures data
signatures <- readr::read_csv("data-example-signatures.csv.zip")

@@

# Create the parallel coordinate plot (if needed)
if (!file.exists("figure-10-1.png")) {

@@

  # Load the figure and then save as an EPS file
  bullet_pcp <- image_read("figure-10-1.png")
  image_write(bullet_pcp, path = "figure-10-1.eps", format = "eps")

@@

# Load and print the plot
knitr::include_graphics("figure-10-1.eps")

@@

# Apply LIME to all but two cases without returning the permutations
if (!file.exists("data-bullet-lime.rds") | !file.exists("data-bullet-explain.rds")){

@@

  # Save the output objects
  saveRDS(object = bullet_lime_noperms, file = "data-bullet-lime.rds")
  saveRDS(object = bullet_explain_noperms, file = "data-bullet-explain.rds")

@@

  # Load the files
  bullet_explain_noperms <- readRDS("data-bullet-explain.rds")

>>>>

# Apply LIME with various tuning parameters to the sine data
if (!file.exists("data/sine-lime-explain.rds")) {

@@

    saveRDS(sine_lime_explain, "data/sine-lime-explain.rds")

@@

    sine_lime_explain <- readRDS("data/sine-lime-explain.rds")

@@

# Load the bullet matching training data and make some adjustments:
#   1. filter out observations known to have tank rash
#   2. exclude features not used to train the rtrees random forest 
#   3. add a case variable
#   4. change the name of the same_source variable to match the test data
#   5. reorder the variables
bullet_train <- readr::read_csv("data/bullet-train.csv.zip") %>%

# Load the bullet test data
bullet_test <- readr::read_csv("data/bullet-test.csv.zip")

@@

# Convert the bullet figure to eps (if needed)
if (!file.exists("figure-static/figure-08-1.eps")) {
  unzip("figure-static/figure-08-1.png.zip")
  bullets <- image_read("figure-static/figure-08-1.png")
  image_write(bullets, path = "figure-static/figure-08-1.eps", format = "eps")
}

# Load and print the plot
knitr::include_graphics("figure-static/figure-08-1.eps")

@@

# Load the signatures data
signatures <- readr::read_csv("data/example-signatures.csv.zip")

@@

# Create the parallel coordinate plot (if needed)
if (!file.exists("figure-static/figure-10-1.png")) {

@@

  # Load the figure and then save as an EPS file
  bullet_pcp <- image_read("figure-static/figure-10-1.png")
  image_write(bullet_pcp, path = "figure-static/figure-10-1.eps", format = "eps")

@@

# Load and print the plot
knitr::include_graphics("figure-static/figure-10-1.eps")

@@

# Apply LIME to all but two cases without returning the permutations
if (!file.exists("data/bullet-lime.rds") | !file.exists("data/bullet-explain.rds")){

@@

  # Save the output objects
  saveRDS(object = bullet_lime_noperms, file = "data/bullet-lime.rds")
  saveRDS(object = bullet_explain_noperms, file = "data/bullet-explain.rds")

@@

  # Load the files
  bullet_explain_noperms <- readRDS("data/bullet-explain.rds")
